---
title: "Barebones FishSET Vignette"
author: "Fishy McFisherperson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Runs discrete choice models.

- User supplies `catch`, `choice`, and `distance` data, plus any other data (`otherdat`) they need to run their chosen likelihood.
- Currently ships with a conditional logit function `clogit`.

## To run models call the `zonal_subroutine` function

The user supplies `catch`, `choice`, and `distance` data. The data `catch` and `choice` should be data frames with dimensions (number of observations) x 1.
The distance data should be a data frame with dimensions (number of observations) x (number of alternatives).
Other data may be something like predicted catch for each alternative (e.g. a data frame with dimensions (number of observations) x (number of alternatives)).
The user supplies initial parameters, optimization options and the likelihood function name, for a total of 7 total inputs.

func <- clogit #function(starts3,dat,otherdat,alts) starting params, dataCompile, otherdat = other data used in likelihood (predicted catches), alts


    For example:  
      initparams <- c(2.5, -0.8) #Initial paramters for revenue then cost.
		optimOpt <- c(100000,1000000,1.00000000000000e-06) #Optimization options for the maximum number of function evaluations, maximum iterations, and the relative tolerance of x.
		func <- clogit #The conditional logit likelihood function.
		
## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
