---
title: "Barebones FishSET Vignette"
author: "Fishy McFishperson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Barebones FishSET Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Runs discrete choice models. If you run into problems you can contact
allen.chen@noaa.gov.

- User supplies `catch`, `choice`, and `distance` data, plus any other data
`otherdat` they need to run their chosen likelihood.
- Currently ships with a conditional logit function `logit_c`, an average catch
logit function `logit_avgcat`, a full information likelihood with correction
function `logit_correction`, an expected profit model with a normally
distributed catch function `epm_normal`, an expected profit model with a
log-normally distributed catch function `epm_lognormal`, and an expected profit
model with a weibull distributed catch function `epm_weibull`.

## Data
The user supplies `catch`, `choice`, and `distance` data. The data `catch` and
`choice` should be dimensions *(number of observations) x 1*.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
zi <- read.csv("zi.csv", header=FALSE)
zi$V1 <- as.numeric(zi$V1)

catch <- read.csv("catch.csv", header=FALSE)

choice <- read.csv("choice.csv", header=FALSE)
choice$V1 <- as.numeric(choice$V1)

predicted_catch <- read.csv("predicted_catch.csv", header=FALSE)
predicted_catch$V3 <- as.numeric(predicted_catch$V3)

distance <- read.csv("distance.csv", header=FALSE)

otherdat <- list(griddat=list(si=as.matrix(predicted_catch)),
    intdat=list(zi=as.matrix(zi)))

library(barebones.FishSET)
```
(Simulated catch and choice data are included in this package i.e.
`data(catch)`.)
```{r, echo=TRUE}
str(catch)
str(choice)
```

The `distance` data should be dimensions *(number of observations) x
(number of alternatives)*. (Simulated distance data is included in this package
i.e. `data(distance)`.)
```{r, echo=TRUE}
str(distance)
```

Other data may be something like `predicted_catch` for each alternative (e.g.
with dimensions *(number of observations) x (number of alternatives)*). This
data could be constructed by the user before estimation of the discrete choice
model, for example by looking at a moving average of historical catches. Below
is an example of predicted catches, as well as a data frame `zi` representing
harvester characteristics. (Simulated harvester characteristics and predicted
data are included in this package i.e. `data(predicted_catch)`.)
```{r, echo=TRUE}
str(otherdat)
```

For the `logit_c` function, any number of grid-specific variables (e.g. expected
catch that varies by location) or interaction variables (e.g. vessel
characteristics that affect how much disutility is suffered by traveling a
greater distance) are allowed. However, the user must place these in `otherdat`
as list objects named `griddat` and `intdat` respectively. Note the variables
within `griddat` and `intdat` have no naming restrictions. Also note that for
this likelihood `griddat` variables are dimension *(number of observations) x
(number of alternatives)*, while `intdat` variables are dimension *(number of
observations) x 1*, to be interacted with the distance to each alternative.

If there are no other data, the user can set `griddat` as ones with dimension
*(number of observations) x (number of alternatives)* and `intdat` variables as
ones with dimension *(number of observations) x 1*. Finally, users can write
their own likelihoods, and this example is specific to the package-supplied
conditional logit (`logit_c`) function (see documentation for other
likelihoods).

## To run models call the `discretefish_subroutine` function

The user supplies initial parameters, optimization options, the likelihood
function name, and the optimization method for a total of 8 inputs. For example:

```{r, echo=TRUE}
initparams <- c(2.5, -0.8)
#Initial paramters for revenue then cost.

optimOpt <- c(1000,1.00000000000000e-08,1,1)
#Optimization options for the maximum iterations, the relative tolerance of x,
    #report frequency, and whether to report iterations.

func <- logit_c
#The conditional logit likelihood function.

methodname <- "BFGS"
#The optimization method chosen, which must be one of the base R `optim`
    #options.
```

The subroutine function takes in 8 inputs and outputs model results in a list
that can be summarized as:

	errorExplain: If it exists, a description of the model error.
	OutLogit: A matrix of coefficients, standard errors, and t-statistics
	optoutput: Optimization information (such as number of function iterations)
	seoutmat2: Standard errors
	MCM: Model comparison metrics (e.g. AIC, BIC)
	H1: The inverse hessian

```{r, echo=TRUE}
results <- discretefish_subroutine(catch,choice,distance,otherdat,initparams,
    optimOpt,func,methodname)
results
```

The true marginal utility from catch in this data-generating process was equal
to 3, and the true disutility from distance was equal to -1. The model estimates
are correct relative to some unknown scale parameter:

```{r, echo=TRUE}
results$OutLogit[1,1]/results$OutLogit[2,1]
```
